{\Huge Supersymmetry} \\ \vspace{5mm} Lecture notes for FYS5190/FYS9190 Supersymmetry

### 2022-01-01 poincare.tex
More N=8 comments

Because of (\ref{eq:QM}) this new algebra is a non-trivial extension of the Poincaré algebra that avoids the no-go theorem. However, in the $Q_a$ we have introduced new operators that (disappointingly) do not correspond to the generators of the gauge groups (which should be related by commutators, not anti-commutators). The gauge group generators {\it can} appear in the algebra if we extend the algebra with a set of $N>1$ new spinors $Q_a^\alpha$, where $\alpha = 1,\ldots,N$. This gives rise to so-called $N>1$ supersymmetries.\footnote{Given a gauge group algebra $[B_i,B_j]=iC_{ij}^kB_k$, we can extended the $N=1$ superalgebra by  the non-trivial commutator $[Q_a^\alpha,B_l]=iS_l^{\alpha\beta}Q_a^\beta$, where $S_l$ are matrix representations of the gauge symmetry group. }
However, this seems impossible to realise in nature at energies accessible in experiments due to an extensive number of extra particles.\footnote{Note that $N>8$ would also include elementary particles with spin greater than 2, which seems to be in contradiction with quantum field theory.} This extension, including the potential for $N>1$, can be proven, under some reasonable assumptions, to be the {\it largest possible} extension of the symmetries of special relativity.

>>>>

Because of (\ref{eq:QM}) this new algebra is a non-trivial extension of the Poincaré algebra that avoids the no-go theorem. This extension can be proven, under some reasonable assumptions, to be the {\it largest possible} extension of the symmetries of special relativity. However, in the $Q_a$ we have introduced new operators that (disappointingly) do not correspond to the generators of the gauge groups, which should in any case  be related by commutators, not anti-commutators. The gauge group generators {\it can} appear in the algebra if we instead extend the algebra with $N>1$ sets of new spinors $Q_a^\alpha$, where $\alpha = 1,\ldots,N$. This gives rise to so-called $N>1$ supersymmetries. Given a gauge group algebra $[B_i,B_j]=iC_{ij}^kB_k$, we can then extended the superalgebra by the non-trivial commutator $[Q_a^\alpha,B_l]=iS_l^{\alpha\beta}Q_a^\beta$, where $S_l$ are matrix representations of the gauge symmetry group, which does not work for $N=1$.

However, the $N>1$ supersymmetries seem impossible to realise in nature due to an extensive number of extra particles that do not conform to the particles and gauge symmetries of the Standard Model. Note that $N>8$ would include elementary particles with spin greater than 2, which seems to be in contradiction with quantum field theory.
The largest consistent supersymmetry, $N=8$, has one spin-2 state (identified with the graviton), 8 spin-$\frac{3}{2}$ states, 28 vector bosons (spin-1),  56 spin-$\frac{1}{2}$ fermions and 70 scalar fields. One fundamental problem with this, besides the plethora of particles, is that the vector bosons here form an $O(8)$ group which is too small to contain the Standard Model $SU(3)\times SU(2)\times U(1)$ symmetry. However, $N=8$, supersymmetry has some very interesting theoretical properties. It is currently unknown whether the theory is finite or not (has infinities that need renormalisation). This has been checked up to four loops, surprisingly without any divergences appearing~\cite{Bern:2009kd}.
